\chapter*{Future developments and conclusion}

Looking to the future, the intention is to significantly expand and enhance the system through the implementation of advanced technologies that promote decentralization and integration with the blockchain. Two key aspects in this evolutionary path include the adoption of IPFS (InterPlanetary File System) to decentralize the parsing process and the integration of MetaMask to enable deployment on a real blockchain.

The implementation of IPFS will be crucial to ensure a more efficient and resilient distribution of information extracted through parsing. This decentralized solution will leverage the peer-to-peer network of IPFS for secure and resilient storage and sharing of data. Such an approach will not only increase the robustness of the system but also provide distributed access to information, reducing dependency on individual central points.

Concurrently, there is a plan to integrate MetaMask to enable deployment on a real blockchain. This implementation will harness the secure and transparent features of a blockchain, ensuring the integrity and traceability of the processed data.

These future developments will lead to a subsequent phase of system evolution, enhancing its efficiency, security, and adaptability to emerging challenges in the context of advanced data management and analysis.

Furthermore, the integration of carbon credits into the system is planned. This feature will allow users to offset the carbon emissions associated with transactions made on the platform, actively contributing to environmental sustainability efforts. The implementation of carbon credits aims to promote eco-sustainable practices and increase awareness of the environmental impacts of the activities carried out within the system.

As a final enhancement, the current front-end, which is currently a mockup, is set to be seamlessly integrated with the blockchain in upcoming developments. These iterations will encompass the implementation of all functionalities for resource visualization, establishing a comprehensive and integrated connection between the user interface and the blockchain.